\chapter{Acknowledgements}

First and foremost, I want to thank David DiVincenzo for being an incredible mentor over the past two years of master’s studies and research. I will be forever grateful for the time you made for me and the many discussions that we have had. You allowed me great freedom, and I always enjoyed the side quests that we had along the way. Your supervision has led me to appreciate a vast range of topics and their historical significance.

I would like to express my sincere gratitude to Rami Barends for your invaluable guidance and support as my second supervisor. You have truly convinced me to pursue the dark side that is experimental physics. Your approachability and readiness to assist with any challenges I faced significantly enriched my research experience, and your willingness to let me gain hands-on experience in the lab was not only instrumental in my learning but also deeply appreciated.

I extend my heartfelt thanks to the group members of PGI-13, for their warmth and generosity. Even though I have not been with you for long, I have been met with nothing but kindness and support whenever I needed assistance in the lab. Being surrounded by such a remarkable group of talented individuals has not only been inspiring but was also a privilege. Your collective spirit and expertise have left a lasting impression on me, and I am excited to witness your future achievements and breakthroughs. 

Last, but not least, I want to thank Aubrey, my parents and my friends for their unconditional love, support, and patience. I would not have reached this point without all of you.
