\chapter{Examples and Applications}\label{chapter:examples}

We will now look at a number of circuits and electromagnetic models to which we apply the methods of the previous two chapters. Before presenting some examples, it is important to make note of what benefits and drawbacks the methods presented in this thesis have in comparison to the immittance formula methods of \cite{solgun_sirf,sherbrooke_sirf}.

In the immittance formula methods, an immittance function is computed at various frequency points -- typically at the desired qubit frequencies in the circuit. Using the computed immittance function at various frequencies, you can estimate the effective qubit couplings, drive crosstalk and amplitudes, and qubit decay rates. However, some issues arise with the estimates in \cite{solgun_sirf} when chips contain strong direct capacitive coupling between the qubits. This is addressed in \cite{sherbrooke_sirf} at the cost of needing to obtain the DC residue of the immittance function to compute the listed quantities. Furthermore, every time you would like to compute a parameter for a new qubit frequency, you are required to also compute the immittance function at that frequency. If you are trying to obtain some initial estimates of these parameters, this may be useful. Still, as frequency tunable qubits and couplers become more common, this may consume a lot of time if working with electromagnetic models.

When dealing with systems containing tunable qubits and couplers, it may be worth spending more time on characterizing the distributed element or electromagnetic models of a superconducting circuit. As we have discussed, we can use vector fitting methods to obtain a rational impedance function which can be translated into a Hamiltonian description of the circuit. From there, all the couplings between the qubits and the resonant modes in the circuit are available to us. Notably, the couplings between the qubits and resonant modes will not be accessible with the immittance formula methods \cite{solgun_sirf, sherbrooke_sirf}. Having this information can help in tweaking a design and estimating parameters that are dependent on these couplings (e.g.\ dispersive shifts of the resonator frequencies (\ref{eq:dispersive_shifts})). Also, this method allows you to easily ``tune'' the qubits to desired frequencies by simply changing the Josephson junction energies at the ports of your impedance. If we obtain the rational impedance through vector fitting once, this effectively removes the need to carry out simulations at a different frequency.

Unfortunately, in order to be able to use the vector fitting methods, we need to be able to compute the impedance at enough frequency points to get a good fit. For multi-qubit circuits, simulations of these electromagnetic models can be prohibitively expensive. However, with the interconnection methods of Section \ref{section:general_network_interconnection}, it may be possible to break up large electromagnetic models into smaller and simpler pieces that can be interconnected, which would decrease the overall simulation time. If the pieces are less complex and contain less resonant modes, we need to sample less points of the impedance function for the fit to accurately represent the model. In addition, these methods can be used on circuit models containing both lumped and distributed elements (e.g.\ combining capacitors, inductors and ideal transmission lines). For these types of models, computing the impedance function is simple and fast over a broad frequency range.

\input{mainmatter/ch4/lumped_distributed.tex}
\input{mainmatter/ch4/electromagnetic.tex}